Generalized Plackett-Luce Likelihoods

### 2022-08-22 inst/jss_hyper3.Rnw
disordR and Fisher information for nonfinishers, a>b>{a,b} etc

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.  The package
includes an \proglang{S3} class \code{hyper3} for this type of object.
Package idiom for creating such objects uses named vectors:

@@

which has a minimum of about $13.9$ at at about $a=0.575$.  We can
compare this with the Fisher information ${\mathcal I}$ for the case
of three distinct runners $a,b,c$, evaluated at its minimum of
$p_a=p_b=p_c=\frac{1}{3}$.  If we observe the complete order
statistic, ${\mathcal I}=\frac{1323}{16}\simeq 82.7$; if we observe
just the winner, ${\mathcal I}=27$, and if we observe just the loser
we have ${\mathcal I}=\frac{16875}{256}\simeq 65.9$.  A brief
discussion is given at \code{inst/fisher\_inf\_PL3.Rmd}.

@@

@@

\section{Formula 1 motor racing: the constructors' championship}

>>>>

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.  The package
includes an \proglang{S3} class \code{hyper3} for this type of object;
extraction and replacement methods use \pkg{disordR}
discipline~\citep{hankin2022}.  Package idiom for creating such
objects uses named vectors:

@@

which has a minimum of about $13.9$ at at about $a=0.575$.  We can
compare this with the Fisher information matrix ${\mathcal I}$, for
the case of three distinct runners $a,b,c$, evaluated at its minimum
of $p_a=p_b=p_c=\frac{1}{3}$.  If we observe the complete order
statistic, $\left|{\mathcal I}\right| =\frac{1323}{16}\simeq 82.7$; if
we observe just the winner, $\left|{\mathcal I}\right|=27$, and if we
observe just the loser we have $\left|{\mathcal
I}\right|=\frac{16875}{256}\simeq 65.9$.  A brief discussion is given
at \code{inst/fisher\_inf\_PL3.Rmd}.

@@

The Fisher information for such observations has a minimum of
$\frac{68}{9}\simeq 7.56$ at $a=\frac{1}{2}$.  An inference problem
for a dataset including nonfinishers will be given below in
section~\ref{f1}.

@@

\section{Formula 1 motor racing: the constructors' championship}\label{f1}
